Toward a Comparable Corpora of Latvian, Russian and English Tweets

### 2017-04-16 paper.tex
Cite software.

\citet{milajevs-griffiths:2016:RepEval}

@@

The initial set of tweets was retrieved using the \texttt{POST status/filter} endpoint of the Twitter Streaming API.\footnote{\url{https://dev.twitter.com/streaming/reference/post/statuses/filter}} The collected tweets had to be geo-located and had to originate from the area of Riga, the capital of Latvia.\footnotemark{}

>>>>

@@

The initial set of tweets was retrieved by subscribing to the \texttt{POST status/filter} endpoint of the Twitter Streaming API\footnote{\url{https://dev.twitter.com/streaming/reference/post/statuses/filter}} with Poultry \cite{dmitrijs_milajevs_2017_546609}. The collected tweets had to be geo-located and had to originate from the area of Riga, the capital of Latvia.\footnotemark{}
